Omics-based Single Step Trait Prediction

### 2017-03-15 paper/manuscript.tex
Update tables and acknowledgments

\section{Materials and Methods}
\subsection{Maize hybrids}
The maize hybrid data set comprises 1,521 hybrids produced in 16 factorial
mating designs between 142 Dent and 103 Flint parent lines \cite{Westhues2017}. 
Best linear unbiased estimates (BLUEs) were computed across all factorials and 
three or more agro-ecologically diverse locations across Germany for six 
agronomically important traits.
All 245 parent lines have pedigree records back to the generation of their 
grandparents or deeper \cite{Westhues2017} and were genotyped using the Illumina 
BeadChip MaizeSNP50 \cite{Ganal2011}.
After filtering for minor allele frequency ($\geq 5$\%), heterozygosity rate
($\leq 5$\%) and call frequency ($\geq 95$\%), missing genotypes were imputed 
using the Beagle software \cite{Browning2009}.
The final number of polymorphic marker loci was 7,013 for parental Dent and
6,212 for parental Flint lines, respectively.
Gene expression data for seedlings seven days after sowing were obtained for a 
subset of 60 parental Dent and 43 parental Flint lines through two-color
hybridizations using a custom 2K microarray (GPL22267) \cite{Westhues2017}.
After applying established normalization procedures 
\cite{Smyth2003,Ritchie2007}, gene expression BLUEs were computed for 1,323 
transcripts in reference to established protocols 
\cite{Smyth2003,Ritchie2007,Frisch2010} using the R-package \textit{limma}
\cite{Ritchie2015a}.

\subsection{Maize diversity panel}
The maize inbred line data set originally comprised 513 maize lines representing 
the global maize diversity and was reduced to the set of tropical and
subtropical lines ($n = 211$) given that it is the largest of the four
pre-classified subgroups \cite{Yang2014}.
All inbred lines were evaluated in five Chinese environments ranging from
$18$ to $30^{\circ}$N and from $102$ to $110^{\circ}$E \cite{Yang2014}.
Best linear unbiased predictors (BLUPs) were calculated for 17 traits of which 
six were used for this study.
MaizeSNP50 BeadChip-data were available for the entire set of lines from the
diversity panel.
Additionally, RNA sequencing was performed for 368 lines on young seedlings 15 
days after sowing.
By exploting identify by descent (IBD) between 49,728 SNPs on the BeadChip 
overlapping with the RNA-seq data, 556,809 high quality SNPs could be inferred 
for these lines \cite{Fu2013,Li2013}.
For the remaining 145 maize lines without RNA-seq data, high density markers
were inferred via projection of IBD regions onto the BeadChip, using this core 
set of markers \cite{Yang2014}.
The same SNP quality checks as for the parental inbred lines of the hybrids
were applied to the 211 inbred lines from the tropical/subtropical subset,
yielding 37,760 SNPs.
Gene expression data were normalized using a normal quantile transformation to
satisfy modelling assumptions \cite{Fu2013}.
A subset of 28,850 annotated genes was available for 149 out of the 211
genotypes and was kept for further analyses \cite{Li2013}.

\subsection{Population structure}
Principal component analyses (PCA) were run on scaled and centered predictor 
matrices using the \emph{pca} function from the R-package \textit{LEA} 
\cite{Frichot2015}.
Estimates of ancestry coefficients were estimated based on sparse nonnegative
matrix factorization algorithms \cite{Frichot2014} using the \emph{snmf} 
function in \textit{LEA}.
Algorithms were run for $K=2, \dots 5$ putative ancestral gene pools with 25
repetitions for each value of $K$. 
For each $K$, only the repetition with the lowest cross-entropy was kept for 
further analyses.

\subsection{Core sampling}
In order to evaluate the influence of the genetic constitution of the set of
genotypes that has only data on one out of two predictors, we generated core 
samples using the R-package \textit{corehunter} \cite{Thachuk2009}.
These core samples were based on the 149 maize inbred lines from the diversity
panel which had gene expression as well as genomic information.
The size of the core set was varied in increments of ten percentage points and 
ranged from 10\% to 90\% of all 149 inbred lines.
For assembling the various core sets, we first computed the Modifed Rogers (MR)
distance between each pair of genotypes and then selected a predefined subset
of genotypes that display maximum average distance between each other.
MR was computed using the \emph{rogers.dist} function from the R-pacakge
\textit{poppr} \cite{Kamvar2015}.

\subsection{Prediction}
\subsubsection{Kernels}
BLUP models are computationally attractive when the number of features $p$
exceeds the number of genotypes $n$ and are equivalent to a selection index
when fixed effects have been accomodated by the dependent variable 
\cite{Mrode2014}.
Depending on the data set, up to three predictors were available for agronomic
trait predictions, namely pedigree data (P), genomic data (G) and
transcriptompic data (T).
The corresponding feature matrix of the $l$-th group of inbred lines and the 
$o$-th predictor ($\mathbf{W}_{lo}$) has dimensions $n \times p$ where $n$
pertains to the number of genotypes in the $l$-th group and $p$ pertains to 
the number of features.
For the diversity panel maize lines, $n$ corresponds to the number of genotypes
whereas, in the case of the hybrid data, $n$ corresponds to the number of
parent lines in the corresponding heterotic group.
In generating kernels for each predictor, all features in $\mathbf{W}_{lo}$ were
centered and standardized to unit variance.
Then, each kernel can be defined as

@@

\subsubsection{Universal breeding value model}
The universal model for breeding values was:

@@

\subsubsection{Single step prediction}
The breeding values in a prediction model are in general given by:
\begin{equation} \label{eq:mrnaebv}
	\mathbf{\tilde{g}} = \mathbf{W}\boldsymbol{\hat{\alpha}},
\end{equation}

@@

\subsubsection{Predictive ability and model validation}
For the validation of our predictions, we employed leave-one-out
cross-validation (LOOCV) routines.
In the case of the diversity panel maize inbred lines, LOOCV was performed by 
using a single genotype as a hold-out sample, which will subsequently be 
predicted, while using all other inbred lines for model training.
This process is repeated until all inbred lines have been used once for testing
and $n - 1$ times for model training.

@@

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 10:35:35 2017
% Script: ./analysis/maizego_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of 211 tropical/subtropical lines from the maize diversity panel.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: no}}\\
snp-mrna & 0.44 (0.0748) & 0.33 (0.1727) & 0.4 (0.0543) & 0.34 (0.0425) & 0.4 (0.0707) & 0.53 (0.0285) \\ 
  snp-none & 0.43 (0.0733) & 0.37 (0.1734) & 0.39 (0.0535) & 0.34 (0.0455) & 0.45 (0.0755) & 0.53 (0.0297) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: yes}}\\
mrna-none & 0.4 (0.0747) & 0.15 (0.1568) & 0.37 (0.0509) & 0.36 (0.0423) & 0.32 (0.0692) & 0.49 (0.0279) \\ 
  snp-none1 & 0.36 (0.0773) & 0.21 (0.1678) & 0.3 (0.0527) & 0.34 (0.0472) & 0.41 (0.078) & 0.45 (0.0302) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 11:11:37 2017
% Script: ./analysis/uhoh_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of maize hybrids} 
\begin{tabular}{rllllll}
  \toprule
 & DMY & DMC & FAT & PRO & STA & SUG \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
ped-none & 0.54 (0.0493) & 0.48 (0.0521) & 0.21 (0.0365) & 0.6 (0.0187) & 0.35 (0.0427) & 0.42 (0.117) \\ 
  snp-none & 0.74 (0.0517) & 0.63 (0.0521) & 0.43 (0.0356) & 0.65 (0.0223) & 0.46 (0.0458) & 0.47 (0.1261) \\ 
  ped-snp & 0.71 (0.054) & 0.57 (0.0545) & 0.35 (0.0375) & 0.62 (0.0235) & 0.39 (0.0478) & 0.42 (0.1298) \\ 
  ped-mrna & 0.73 (0.056) & 0.53 (0.0594) & 0.35 (0.0398) & 0.61 (0.0254) & 0.31 (0.0504) & 0.37 (0.1396) \\ 
  snp-mrna & 0.75 (0.0533) & 0.61 (0.0553) & 0.43 (0.0374) & 0.65 (0.0239) & 0.44 (0.048) & 0.44 (0.1342) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
mrna-none & 0.75 (0.0552) & 0.34 (0.0619) & 0.4 (0.0412) & 0.47 (0.0293) & 0.16 (0.0496) & 0.27 (0.1447) \\ 
  ped-none1 & 0.46 (0.0469) & 0.53 (0.05) & 0.23 (0.0368) & 0.46 (0.0234) & 0.38 (0.0391) & 0.34 (0.1316) \\ 
  snp-none1 & 0.67 (0.0534) & 0.47 (0.0552) & 0.43 (0.0384) & 0.48 (0.027) & 0.36 (0.0457) & 0.35 (0.132) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 11:36:08 2017
% Script: ./analysis/maizego_core_fraction_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for different core sets from the tropical/subtropical material of the maize diversity panel.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
snp-mrna & 0.44 (0.0748) & 0.33 (0.1727) & 0.4 (0.0543) & 0.34 (0.0425) & 0.4 (0.0707) & 0.53 (0.0285) \\ 
  snp-none & 0.43 (0.0733) & 0.37 (0.1734) & 0.39 (0.0535) & 0.34 (0.0455) & 0.45 (0.0755) & 0.53 (0.0297) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
mrna-none\_1.0 & 0.4 (0.0747) & 0.15 (0.1568) & 0.37 (0.0509) & 0.36 (0.0423) & 0.32 (0.0692) & 0.49 (0.0279) \\ 
  snp-mrna\_0.3 & 0.36 (0.0711) & 0.2 (0.1566) & 0.28 (0.0503) & 0.37 (0.044) & 0.42 (0.0736) & 0.5 (0.028) \\ 
  snp-mrna\_0.4 & 0.39 (0.0697) & 0.2 (0.1558) & 0.33 (0.0486) & 0.35 (0.0428) & 0.38 (0.0727) & 0.52 (0.028) \\ 
  snp-mrna\_0.5 & 0.41 (0.0671) & 0.16 (0.1549) & 0.31 (0.0486) & 0.4 (0.0414) & 0.44 (0.0748) & 0.49 (0.0278) \\ 
  snp-mrna\_0.6 & 0.4 (0.0739) & 0.13 (0.1563) & 0.27 (0.0497) & 0.37 (0.0417) & 0.42 (0.075) & 0.55 (0.0272) \\ 
  snp-mrna\_0.7 & 0.37 (0.0734) & 0.1 (0.1555) & 0.31 (0.0508) & 0.37 (0.0422) & 0.33 (0.0755) & 0.52 (0.028) \\ 
  snp-mrna\_0.8 & 0.4 (0.0774) & 0.21 (0.1581) & 0.36 (0.0515) & 0.41 (0.0458) & 0.29 (0.0737) & 0.49 (0.0288) \\ 
  snp-mrna\_0.9 & 0.39 (0.0792) & 0.21 (0.1692) & 0.38 (0.0561) & 0.41 (0.0459) & 0.29 (0.075) & 0.49 (0.0311) \\ 
  snp-none\_1.0 & 0.36 (0.0773) & 0.21 (0.1678) & 0.3 (0.0527) & 0.34 (0.0472) & 0.41 (0.078) & 0.45 (0.0302) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

@@

\section{Acknowledgments} 
We thank the staff of the Agricultural Experimental Research station,
University of Hohenheim, for excellent technical assistance in
conducting the field experiments. We are indebted to the group of R.
Fries from Technische Universit{\"a}t M{\"u}nchen for the SNP genotyping of the
parent inbred lines, to X. Mi for his assistance in preparing auxiliary
figures based on the Mathematica software, to C. Zenke for advice on the
computation of transcriptomic BLUEs and to P. Schopp for advice on
prediction models. The authors acknowledge support by the state of
Baden-W{\"u}rttemberg through bwHPC. This project was funded by the German
Federal Ministry of Education and Research (BMBF) within the projects
OPTIMAL (FKZ: 0315958B,0315958F), SYNBREED (FKZ: 0315528D) and by the
German Research Foundation (DFG, Grants No. ME 2260/5-1 and SCHO 764/6-1).
Financial support for M.W. was provided by the Fiat Panis foundation, Ulm,
Germany.

>>>>

\section{Materials and Methods}
\Genetics2level{Maize hybrids}
The maize hybrid data set comprises 1,521 hybrids produced in 16 factorial
mating designs between 142 Dent and 103 Flint parent lines \cite{Westhues2017}. 
Best linear unbiased estimates (BLUEs) were computed across all factorials and 
three or more agro-ecologically diverse locations across Germany for six 
agronomically important traits.
All 245 parent lines have pedigree records back to the generation of their 
grandparents or deeper \cite{Westhues2017} and were genotyped using the Illumina 
BeadChip MaizeSNP50 \cite{Ganal2011}.
After filtering for minor allele frequency ($\geq 5$\%), heterozygosity rate
($\leq 5$\%) and call frequency ($\geq 95$\%), missing genotypes were imputed 
using the Beagle software \cite{Browning2009}.
The final number of polymorphic marker loci was 7,013 for parental Dent and
6,212 for parental Flint lines, respectively.
Gene expression data for seedlings seven days after sowing were obtained for a 
subset of 60 parental Dent and 43 parental Flint lines through two-color
hybridizations using a custom 2K microarray (GPL22267) \cite{Westhues2017}.
After applying established normalization procedures 
\cite{Smyth2003,Ritchie2007}, gene expression BLUEs were computed for 1,323 
transcripts in reference to established protocols 
\cite{Smyth2003,Ritchie2007,Frisch2010} using the R-package \textit{limma}
\cite{Ritchie2015a}.

\Genetics2level{Maize diversity panel}
The maize inbred line data set originally comprised 513 maize lines representing 
the global maize diversity and was reduced to the set of tropical and
subtropical lines ($n = 211$) given that it is the largest of the four
pre-classified subgroups \cite{Yang2014}.
All inbred lines were evaluated in five Chinese environments ranging from
$18$ to $30^{\circ}$N and from $102$ to $110^{\circ}$E \cite{Yang2014}.
Best linear unbiased predictors (BLUPs) were calculated for 17 traits of which 
six were used for this study.
MaizeSNP50 BeadChip-data were available for the entire set of lines from the
diversity panel.
Additionally, RNA sequencing was performed for 368 lines on young seedlings 15 
days after sowing.
By exploting identify by descent (IBD) between 49,728 SNPs on the BeadChip 
overlapping with the RNA-seq data, 556,809 high quality SNPs could be inferred 
for these lines \cite{Fu2013,Li2013}.
For the remaining 145 maize lines without RNA-seq data, high density markers
were inferred via projection of IBD regions onto the BeadChip, using this core 
set of markers \cite{Yang2014}.
The same SNP quality checks as for the parental inbred lines of the hybrids
were applied to the 211 inbred lines from the tropical/subtropical subset,
yielding 37,760 SNPs.
Gene expression data were normalized using a normal quantile transformation to
satisfy modelling assumptions \cite{Fu2013}.
A subset of 28,850 annotated genes was available for 149 out of the 211
genotypes and was kept for further analyses \cite{Li2013}.

\Genetics2level{Population structure}
Principal component analyses (PCA) were run on scaled and centered predictor 
matrices using the \emph{pca} function from the R-package \textit{LEA} 
\cite{Frichot2015}.
Estimates of ancestry coefficients were estimated based on sparse nonnegative
matrix factorization algorithms \cite{Frichot2014} using the \emph{snmf} 
function in \textit{LEA}.
Algorithms were run for $K=2, \dots 5$ putative ancestral gene pools with 25
repetitions for each value of $K$. 
For each $K$, only the repetition with the lowest cross-entropy was kept for 
further analyses.

\Genetics2level{Core sampling}
In order to evaluate the influence of the genetic constitution of the set of
genotypes that has only data on one out of two predictors, we generated core 
samples using the R-package \textit{corehunter} \cite{Thachuk2009}.
These core samples were based on the 149 maize inbred lines from the diversity
panel which had gene expression as well as genomic information.
The size of the core set was varied in increments of ten percentage points and 
ranged from 10\% to 90\% of all 149 inbred lines.
For assembling the various core sets, we first computed the Modifed Rogers (MR)
distance between each pair of genotypes and then selected a predefined subset
of genotypes that display maximum average distance between each other.
MR was computed using the \emph{rogers.dist} function from the R-pacakge
\textit{poppr} \cite{Kamvar2015}.

\Genetics2level{Prediction}
\subsection{Kernels}
BLUP models are computationally attractive when the number of features $p$
exceeds the number of genotypes $n$ and are equivalent to a selection index
when fixed effects have been accomodated by the dependent variable 
\cite{Mrode2014}.
Depending on the data set, up to three predictors were available for agronomic
trait predictions, namely pedigree data (P), genomic data (G) and
transcriptompic data (T).
The corresponding feature matrix of the $l$-th group of inbred lines and the 
$o$-th predictor ($\mathbf{W}_{lo}$) has dimensions $n \times p$ where $n$
pertains to the number of genotypes in the $l$-th group and $p$ pertains to 
the number of features.
For the diversity panel maize lines, $n$ corresponds to the number of genotypes
whereas, in the case of the hybrid data, $n$ corresponds to the number of
parent lines in the corresponding heterotic group.
In generating kernels for each predictor, all features in $\mathbf{W}_{lo}$ were
centered and standardized to unit variance.
Then, each kernel can be defined as

@@

\subsection{Universal breeding value model}
The universal model for breeding values was:

@@

\subsection{Single step prediction}
The breeding values in a prediction model are in general given by:
\begin{equation} \label{eq:mrnaebv}
	\mathbf{\tilde{g}} = \mathbf{W}\boldsymbol{\hat{\alpha}},
\end{equation}

@@

\subsection{Predictive ability and model validation}
For the validation of our predictions, we employed leave-one-out
cross-validation (LOOCV) routines.
In the case of the diversity panel maize inbred lines, LOOCV was performed by 
using a single genotype as a hold-out sample, which will subsequently be 
predicted, while using all other inbred lines for model training.
This process is repeated until all inbred lines have been used once for testing
and $n - 1$ times for model training.

@@

\begin{figure}[H]
\centering
\includegraphics{./tables_figures/uhoh_dent_flint_pca.pdf}
\caption{
  Principal component (PC) analysis of the two heterotic groups of the maize 
  hybrids.
  All inbred lines, which are covered by genomic and transcriptomic features
  are depicted as orange triangles whereas genotypes for which only genomic
  information are available are depicted as blue dots.
}
\label{fig:UHOH-PCA}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics{./tables_figures/maizego_admixture_pca.pdf}
\caption{
  (\textbf{A}) Ancestry coefficients for 211 tropical/subtropical inbred lines
  from the maize diversity panel considering $K=2 \dots 5$ ancestral
  populations.
  (\textbf{B}) Principal component analysis for nine different core sets of the
  set of tropical/subtropical maize inbred lines.
  For each size of the core set, its members are plotted as orange dots whereas 
  all genotypes that are not elements of the cores sets (\textit{i.e.},
  'Complement') are depicted as blue dots.
}
\label{fig:PopStructure}
\end{figure}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 17:33:34 2017
% Script: ./analysis/maizego_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of 211 tropical/subtropical lines from the maize diversity panel.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
G & 0.43 (0.07) & 0.37 (0.17) & 0.39 (0.05) & 0.34 (0.05) & 0.45 (0.08) & 0.53 (0.03) \\ 
  GT & 0.44 (0.07) & 0.33 (0.17) & 0.4 (0.05) & 0.34 (0.04) & 0.4 (0.07) & 0.53 (0.03) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
G & 0.36 (0.08) & 0.21 (0.17) & 0.3 (0.05) & 0.34 (0.05) & 0.41 (0.08) & 0.45 (0.03) \\ 
  T & 0.4 (0.07) & 0.15 (0.16) & 0.37 (0.05) & 0.36 (0.04) & 0.32 (0.07) & 0.49 (0.03) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 17:31:28 2017
% Script: ./analysis/uhoh_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of maize hybrids} 
\begin{tabular}{rllllll}
  \toprule
 & DMY & DMC & FAT & PRO & STA & SUG \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
T & 0.75 (0.0552) & 0.34 (0.0619) & 0.4 (0.0412) & 0.47 (0.0293) & 0.16 (0.0496) & 0.27 (0.1447) \\ 
  P & 0.54 (0.0493) & 0.48 (0.0521) & 0.21 (0.0365) & 0.6 (0.0187) & 0.35 (0.0427) & 0.42 (0.117) \\ 
  G & 0.74 (0.0517) & 0.63 (0.0521) & 0.43 (0.0356) & 0.65 (0.0223) & 0.46 (0.0458) & 0.47 (0.1261) \\ 
  PG & 0.71 (0.054) & 0.57 (0.0545) & 0.35 (0.0375) & 0.62 (0.0235) & 0.39 (0.0478) & 0.42 (0.1298) \\ 
  PT & 0.73 (0.056) & 0.53 (0.0594) & 0.35 (0.0398) & 0.61 (0.0254) & 0.31 (0.0504) & 0.37 (0.1396) \\ 
  GT & 0.75 (0.0533) & 0.61 (0.0553) & 0.43 (0.0374) & 0.65 (0.0239) & 0.44 (0.048) & 0.44 (0.1342) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
P & 0.46 (0.0469) & 0.53 (0.05) & 0.23 (0.0368) & 0.46 (0.0234) & 0.38 (0.0391) & 0.34 (0.1316) \\ 
  G & 0.67 (0.0534) & 0.47 (0.0552) & 0.43 (0.0384) & 0.48 (0.027) & 0.36 (0.0457) & 0.35 (0.132) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 17:36:40 2017
% Script: ./analysis/maizego_core_fraction_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for different core sets from the tropical/subtropical material of the maize diversity panel.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
G & 0.43 (0.0733) & 0.37 (0.1734) & 0.39 (0.0535) & 0.34 (0.0455) & 0.45 (0.0755) & 0.53 (0.0297) \\ 
  GT & 0.44 (0.0748) & 0.33 (0.1727) & 0.4 (0.0543) & 0.34 (0.0425) & 0.4 (0.0707) & 0.53 (0.0285) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
G\_1.0 & 0.36 (0.0773) & 0.21 (0.1678) & 0.3 (0.0527) & 0.34 (0.0472) & 0.41 (0.078) & 0.45 (0.0302) \\ 
  GT\_0.3 & 0.36 (0.0711) & 0.2 (0.1566) & 0.28 (0.0503) & 0.37 (0.044) & 0.42 (0.0736) & 0.5 (0.028) \\ 
  GT\_0.4 & 0.39 (0.0697) & 0.2 (0.1558) & 0.33 (0.0486) & 0.35 (0.0428) & 0.38 (0.0727) & 0.52 (0.028) \\ 
  GT\_0.5 & 0.41 (0.0671) & 0.16 (0.1549) & 0.31 (0.0486) & 0.4 (0.0414) & 0.44 (0.0748) & 0.49 (0.0278) \\ 
  GT\_0.6 & 0.4 (0.0739) & 0.13 (0.1563) & 0.27 (0.0497) & 0.37 (0.0417) & 0.42 (0.075) & 0.55 (0.0272) \\ 
  GT\_0.7 & 0.37 (0.0734) & 0.1 (0.1555) & 0.31 (0.0508) & 0.37 (0.0422) & 0.33 (0.0755) & 0.52 (0.028) \\ 
  GT\_0.8 & 0.4 (0.0774) & 0.21 (0.1581) & 0.36 (0.0515) & 0.41 (0.0458) & 0.29 (0.0737) & 0.49 (0.0288) \\ 
  GT\_0.9 & 0.39 (0.0792) & 0.21 (0.1692) & 0.38 (0.0561) & 0.41 (0.0459) & 0.29 (0.075) & 0.49 (0.0311) \\ 
  T\_1.0 & 0.4 (0.0747) & 0.15 (0.1568) & 0.37 (0.0509) & 0.36 (0.0423) & 0.32 (0.0692) & 0.49 (0.0279) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

@@

\section{Acknowledgments} 
This project was funded by the German Federal Ministry of Education and 
Research (BMBF) within the projects OPTIMAL (FKZ: 0315958B,0315958F),
SYNBREED (FKZ: 0315528D) and by the German Research Foundation 
(DFG, Grants No. ME 2260/5-1 and SCHO 764/6-1).
The authors acknowledge support by the state of Baden-W{\"u}rttemberg through 
bwHPC.
Financial support for M.W. was provided by the Fiat Panis foundation, Ulm,
Germany.
